---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# interpreteffect

<!-- badges: start -->
<!-- badges: end -->

## Overview

interpreteffect is an R package that provides a Shiny app to visualize and interpret effect sizes in psychological and behavioral research. The app helps researchers interpret effect sizes through interactive visualizations.

You can install the development version of interpreteffect from [GitHub](https://github.com/) with:


```{r, , eval = FALSE}
# Install interpreteffect from GitHub
remotes::install_github("PaulRiesthuis/interpreteffect")
```

## Running the Shiny App

To launch the Shiny app, use:

```{r, , eval = FALSE}
library(interpreteffect)

# Then run: 
interpreteffect::app()
```


## Features
- Interactive effect size visualizations

- Comparison of different statistical models

- Customizable parameters for analysis

- User-friendly interface for researchers

